Hector Permafrost

### 2019-05-30 analysis/paper/paper.Rmd
Add current figures to paper

```{r fig-parameter-distribution, fig.cap = param_dist_cap}
param_dist_cap <- paste(
  "Input parameter distributions."
)
readd(draws_plot)
```

@@

>>>>

```{r fig-parameter-distribution, fig.cap = param_dist_cap}
param_dist_cap <- paste(
  "Input parameter distributions for global Hector."
)
readd(draws_plot)
```

@@

## Global Hector

```{r fig-global-timeseries, fig.cap = global_ts_cap, fig.dim = c(10, 8)}
global_ts_cap <- paste(
  "Time series of Hector outputs for different parameter combinations."
)
readd(ts_both)
```

```{r fig-global-scatter, fig.cap = global_scatter_cap, fig.dim = c(8, 5)}
global_scatter_cap <- paste(
  "Hector outputs at 2100 as a function of input parameter values."
)
readd(scatter_both)
```

```{r fig-global-sensitivity, fig.cap = global_sensitivity_cap, fig.dim = c(5, 5)}
global_sensitivity_cap <- paste(
  "Sensitivity and variance decomposition analysis for global Hector."
)
readd(sensitivity_plot)
```

## Permafrost as a biome

## Permafrost methane emissions
